An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 indicators/paper/paper.tex

The indicators that are available in the COVIDcast API have been used in
dashboards produced by COVID Act Now \cite{CovidActNow}, COVID Exit Strategy
\cite{CovidExitStrategy}, and others; to inform the Delphi, DeepCOVID
\cite{Rodriguez:2021}, and the Institute for Health Metrics and Evaluation
(IHME) \cite{IHMEProj} COVID forecasting models; in various federal and state
government reports and analyses; and in a range of news stories. Aside from
operational use in decision-making and forecasting, they have also facilitated
numerous analyses studying the impacts of COVID-19 on the public, the
effectiveness of policy interventions, and factors that influenced the spread of
the pandemic \cite{Adjodah:2021, Pierri:2021, Jewell:2021, Chakrabarti:2020,
  Doerr:2021}. The API currently serves hundreds of thousands of requests to
hundreds of users every day.

@@

As a further example, Figure~\ref{fig:bexar_compare} displays data from Bexar
County, Texas (which contains San Antonio) during July 2020. On July 16, 2020,
San Antonio reported 4,810 backlogged cases after reporting problems prevented
them from being reported over the past two weeks \cite{Palacios:2021}, resulting
in a clearly visible spike in the left-hand panel of
Figure~\ref{fig:bexar_compare} (case data from JHU CSSE, smoothed using a 7-day
trailing average). Meanwhile, Delphi's COVID Trends and Impact Survey averaged
around 350 responses per day in Bexar County over the same time period, and was
able to estimate the fraction of the population who know someone in their
community with COVID-Like Illness (CLI). As we can see in the right-hand panel
of Figure~\ref{fig:bexar_compare}, this signal was not affected by Bexar
County's reporting problems and, as shown in the last subsection, it is (in
general) highly correlated with case rates, providing an alternate stream of
data about COVID activity unaffected by backlogs. Similar reporting problems
have occurred in many jurisdictions across the United States, making it valuable
to cross-check against external sources not part of the same reporting systems.

@@

\acknow{We thank Carrie Reed, Matt Biggerstaff, Michael Johansson, Rachel
  Slayton, Velma Lopez, Jo Walker and others on the CDC COVID-19 Modeling Team;
  Hal Varian, Brett Slatkin, and others on Google's Surveys team and
  Google.org's CMU-Delphi Fellowship team; Curtiss Cobb and others on Facebook's   
  Demography and Survey Science, Data for Good and Health teams; Alex Smola and
  others at Amazon Web Services; Tim Suther and others at Change Healthcare;
  Paul Nielsen and others at Optum; and John Tamerius and others at Quidel.
  This material is based on work supported by gifts from Facebook, Google.org,
  the McCune Foundation, and Optum; Centers for Disease Control and Prevention
  (CDC) grant U01IP001121; National Science Foundation Graduate Research
  Fellowship Program (NSF GRFP) award DGE1745016; and the Center for Machine
  Learning and Health (CMLH) at Carnegie Mellon University.}

>>>>

The indicators that are available in the COVIDcast API have been used in
dashboards produced by COVID Act Now \cite{CovidActNow}, COVID Exit Strategy
\cite{CovidExitStrategy}, and others; to inform the Delphi, DeepCOVID
\cite{Rodriguez:2021}, and the Institute for Health Metrics and Evaluation
(IHME) \cite{IHMEProj} COVID forecasting models; in various federal and state
government reports and analyses; and in a range of news stories. Aside from
operational use in decision-making and forecasting, they have also facilitated
numerous analyses studying the impacts of COVID-19 on the public, the
effectiveness of policy interventions, and factors that influenced the spread of
the pandemic \cite{Adjodah:2021, Pierri:2021, Jewell:2021, Chakrabarti:2020,
  Doerr:2021}. The API currently serves hundreds of thousands of requests to
thousands of users every day.

@@

As a further example, Figure~\ref{fig:bexar_compare} displays data from Bexar
County, Texas (which contains San Antonio) during July 2020. On July 16, 2020,
San Antonio reported 4,810 backlogged cases after reporting problems prevented
them from being reported over the past two weeks \cite{Palacios:2021}, resulting
in a clearly visible spike in the left-hand panel of the figure (case data from
JHU CSSE, smoothed using a 7-day trailing average). Meanwhile, Delphi's COVID
Trends and Impact Survey averaged around 350 responses per day in Bexar County
over the same time period, and was able to estimate the fraction of the
population who know someone in their local community with COVID-Like Illness
(CLI). As we can see in the right-hand panel of the figure, this signal was not
affected by Bexar County's reporting problems and, as shown in the last
subsection, it is (in general) highly correlated with case rates, providing an
alternate stream of data about COVID activity unaffected by backlogs. Similar
reporting problems have occurred in many jurisdictions across the United States,
making it valuable to cross-check against external sources not part of the same
reporting systems.

@@

\acknow{We thank Carrie Reed, Matt Biggerstaff, Michael Johansson, Rachel
  Slayton, Velma Lopez, Jo Walker and others on the CDC COVID-19 Modeling Team; 
  Hal Varian, Brett Slatkin, and others on Google's Surveys team;
  Erin Hattersley, Rasmi Elasmar, and others at Google.org; 
  Evgeniy Gabrilovich and others on Google's Health team; 
  Curtiss Cobb and others on Facebook's  Demography and Survey Science, Data for
  Good and Health teams; 
  Alex Smola and others at Amazon Web Services;
  Tim Suther and others at Change Healthcare;
  Paul Nielsen and others at Optum; 
  John Tamerius and others at Quidel; and
  Ross Epstein and others at SafeGraph.
  This material is based on work supported by gifts from Facebook, Google.org,
  the McCune Foundation, and Optum; Centers for Disease Control and Prevention
  (CDC) grant U01IP001121; National Science Foundation Graduate Research
  Fellowship Program (NSF GRFP) award DGE1745016; and the Center for Machine
  Learning and Health (CMLH) at Carnegie Mellon.}
